\newpage

\section{Conclusion and Future Work}\label{Conclusion and Future Work}

N2Sky is presented as a novel cloud-based virtual community platform, which allows sharing and exchanging of neural network knowledge and computing resources. Today, N2Sky is tightly coupled with new technologies, which aims to increase scalability, extensibility, portability and performance.

On the infrastructure and application level of this platform, is implemented the scalable micro services architecture. The cloud environment monitoring is implemented for the system administrator. Additionally, the customized alerting system helps to control the environment without constant monitoring by a human.  

It has a modern, user-friendly interface and gives positive user experience. The N2Sky platform was tested on desktop PCs, mobile devices and tablets. Because the design is user-oriented, a step-by-step processing workflow of actions was easy for all types of users. 

There are already packaged solutions located in the neural networks and models respository, which can be easily reused in own projects. The creation of an own neural network from existing paradigms is possible via the N2Sky user interface without deep knowledge in this field.

The new ViNNSL template format gave the contributors a new and simple way on how to describe and set all needed data about a neural network into one file. The ViNNSL template is dynamic and extendable, can be modified on one side and it will be reflected automatically across all the N2Sky services. 

In the future, N2Sky can be extended from the neural network domain to an arbitrary machine learning. Hereby, the ViNNSL template extension and scalable microservices N2Sky architecture can be useful for future work.