%\begin{verbatim}

%

%\end{verbatim}
\thispagestyle{empty}

\section*{Abstract}

The master thesis encapsulates multiple topics in artificial neural networks, language specification for neural networks, cloud computing, microservices, system monitoring, web and infrastructure design. It is based on the concept of the implementation of the ViNNSL (Vienna Neural Network Specification Language) \cite{Beran2008} and on the original idea of the platform for the artificial neural network simulation environment N2Sky \cite{ravo} and N2Grid \cite{schikuta2004n2grid}. 

This thesis presents N2Sky as a reimagining novel system, which provides a virtual collaboration platform to the computational intelligence community. N2Sky is cloud-based platform and it implements Neural Network as a Service approach, which allows users to share and exchange neural network knowledge resources.

The user-centered intuitive design is a fundamental requirement for N2Sky. The platform supports different types of stakeholders and can be used on any device. As arbitrary users, N2Sky is a learning platform, which provides existing neural network solution to a given problem. As neural network engineers, creating and training neural networks from existing paradigm and as contributors, developing own neural network paradigms and publishing it for the community. For every user assign personal and customizable dashboard, so that he has it is own way to interact with the N2Sky application. 

The main purpose of the master thesis to make production ready application. N2Sky implements microservices architecture on infrastructure as well as on application level. To make the system stable, the customized monitoring and alerting system was created, which allows the system administrator to control the environment directly from the N2Sky user interface. Additionally, it was decided to implement ViNNSL template, which based on ViNNSL 2.0 \cite{ijcnn15}, in order to support transparent neural networks workflow across the entire application.

%\section*{Conclusion}
