\section{Vienna Neural Network Specification Language}\label{ViNNSL 2.0 extended}

In this chapter will be described the history of the ViNNSL language, its development, and new features, which are applied in the current N2Sky System.

\subsection{ViNNSL Development}\label{ViNNSL Development}
Vienna Neural Network Specification Language (ViNNSL) is the language, which is used for the description of the semantic and behaviour of the neural network paradigm. ViNNSL gives the possibility to create dynamic services, which can differentiate the behaviour. The ViNNSL has been seen as a semantic language standard. The language uses schemas, which help users to describe attributes like service capabilities, semantic, functions, and parameters \cite{Beran2008}.

ViNNSL consist of five parts:
\begin{itemize}
\item Description Schema
\item Definition Schema
\item Data Schema
\item Result Schema
\end{itemize}

This approach with multiple schemas was used in Neural Network Cube (N2Grid) System. This system is a web-based neural network simulator used by students and researchers \cite{schikuta2004n2grid}. Today, N2Sky is the follower of the N2Grid ideas. 

In 2015, the ViNNSL 2.0 was released, which was an extension of the previous version \cite{ijcnn15}. Basically, almost nothing changed, only additional fields were added:
\begin{itemize}
\item \emph{Creator}
\item \emph{Problem Domain}
\item \emph{Propagation Type}
\item \emph{Learning Type}
\item \emph{Application Field}
\item \emph{Network Type}
\item \emph{Problem Type}
\item \emph{Execution Environment} The idea was proposed by the concept of the N2Grid \cite{schikuta2004n2grid}. It is possible to define the environment, which is needed for particular neural network instances. 
\item \emph{Execution Type.} Neural networks will be executed either sequential or parallel. Additionally, the neural networks architecture and metadata could be defined. 
\item \emph{Result Schema} became part of the ViNNSL Description. Earlier, it was a separated schema, but the data schema and instance schema still remained the same.
\item \emph{Parameters} The user could define input as well as output parameters. The training file and the file type could also be determined in the schema.
\end{itemize}

\subsection{ViNNSL Template}\label{ViNNSL Template}

After studying ViNNSL with its extension, it was decided to simplify all schemas and most importantly adapt it to the current N2Sky System.

The idea behind is to use the ViNNSL template, which has additional fields from ViNNSL 2.0. The fields can be fully processed and be removed after creating the neural network. No more extra objects or fields in other application. ViNNSL template allows users to apply the ViNNSL language across the whole N2Sky platform. The detailed information is shown in \autoref{A}

\subsubsection{Metadata template}\label{Metadata template}

As before mentioned, the ViNNSL 2.0 contains metadata about the user and neural network.

\begin{lstlisting}[caption=ViNNSL template metadata]
...
	"problemDomain": {
		"propagationType": {
			"value": null,
			"possibleValues": ["feedforward"],
			"learningType": {
				"value": null,
				"possibleValues": ["definedconstructed", 
				"trained", "supervised", "usupervised", "linear"]
			}
		},
		"applicationField": {
			"value": null,
			"possibleValues": ["AccFin", "HealthMed", "Marketing",
			 "Retail", "Insur", "Telecom", "Operations", "EMS"]
		},
		"problemType": {
			"value": null,
			"possibleValues": ["Classifiers", "Approximators",
			 "Memory", "Optimisation", "Clustering"]
		},
		"networkType": "Backpropagation"
	}
...
\end{lstlisting}

From the code above, it is possible to spot additional values:
\begin{itemize}
\item \emph{value} is the default value of the object. 
\item \emph{possibleValues} parameter, which contains an array of possible value. The user can choose one of the value. 
\end{itemize}

This approach not only helps to add templating into the current ViNNSL schema, but also adds some rules upon it:
\begin{itemize}
\item If the default value is set and there are no more values under "possibleValues" parameter, then the value is impossible to change.
\item If there is no value for "possibleValues" and "value" fields, then the user can type a customized value.
\item If the "value" has some parameter and "possibleValues" field is also not empty, it means the "value" parameter is the default value and it can be changed by "possibleValues".
\end{itemize}

\subsubsection{Environment}\label{Environment}

In previous versions of the ViNNSL language was possible to define the execution environment. This possibility is still available, but some additional values were added in order to apply the templating approach. 

In the current version of N2Sky, the user can deploy neural network on the N2Sky cloud as well as on the private cloud. The "endpoints" parameter was added.

\begin{lstlisting}[caption=ViNNSL template environment]
...
    "endpoints": [{
        "name": "train",
        "endpoint": null
    }, {
        "name": "test",
        "endpoint": null
    }]
...
\end{lstlisting}

Since it is an array parameter, it gives room for adding new endpoints in case that it will be needed in future versions of N2Sky.

\subsubsection{Neural Network Structure Template}\label{Neural Network Structure Template}

The structure of the neural network was also changed. The template looks pretty empty, but from that is possible to generate any type of structure based on ViNNSL language. 

\begin{lstlisting}[caption=ViNNSL template structure]
...
"structure": {
		"inputLayer": {
			"result": {
				"nodesId": []
			},
			"config": {
				"dimensions": {
					"min": 1,
					"max": 1
				},
				"size": {
					"min": 960,
					"max": 960
				}
			}
		},
		"hiddenLayer": {
			"result": {
				"dimensions": [{
					"id": null,
					"nodesId": []
				}]
			},
			"config": {
				"dimensions": {
					"min": 1,
					"max": 1
				},
				"size": {
					"min": 960,
					"max": 960
				}
			}
		},
		"outputLayer": {
			"result": {
				"nodesId": []
			},
			"config": {
				"dimensions": {
					"min": 1,
					"max": 1
				},
				"size": {
					"min": 960,
					"max": 960
				}
			}
		},
...
\end{lstlisting}

The structure contains input, hidden and output layer. The hidden layer has "dimensions" parameter, which allows creating multiple hidden layers.

Every layer has "config" property, which shows how many dimensions can be used. This config is scalable and additional configuration can be added. 
 
 Furthermore, every layer has a number of nodes, namely the neurons id.  
 
 In the structure, it is important to define the connections between nodes. 
 

 \begin{lstlisting}[caption=ViNNSL template connections]
...
		"connections": {
			"fullyConnected": {
				"isConnected": null
			},
			"shortcuts": {
				"isConnected": null,
				"connections": [{
					"from": null,
					"to": null,
					"isFullConnected": null
				}]
			}
		}
	}
...
\end{lstlisting}

There are few types of connections:
\begin{itemize}
\item \emph{fullyConnected} parameter, which has boolean "isConnected" in case that the neural network is fully connected or not.
\item \emph{shortcuts} is a parameter, which also has boolean flag parameter. If there are any types of the shortcuts, it will be set to true. Inside of this parameter, the array field "connections" has "from" and "to" nodes id parameter. In case that the full connection remains the same "isFullConnected" will be set to true.
\end{itemize}

\subsubsection{Parameters Template}\label{Parameters Template}

 The templating was also applied to the input parameters. The structure of the template is pretty similar to metadata template.

 \begin{lstlisting}[caption=ViNNSL template input parameters]
...
"parameters": {
		"input": [
			{
				"parameter": "activationFunction",
				"defaultValue": "sigmoid",
				"possibleValues": ["sigmoid", "relu", "softmax"]
			},
			{
				"parameter": "activationFunctionHidden",
				"defaultValue": "relu",
				"possibleValues": ["sigmoid", "relu"]
			},
...
\end{lstlisting}

Additionally, in this template the "parameter" field is used. This field defines an actual input parameter and has to be unique.

The output parameter is fixed and can not be changed. This parameter will be used for trained model evaluation in case that the user does not want to type his own testing data.

The training file information is also defined under parameters and can be changed only by the neural network owner.


\subsection{ViNNSL Generation}\label{ViNNSL Generation}

After the neural network contributor user fills out the ViNNSL template, the user can generate the ViNNSL Description schema. This schema will be used for neural network training. The generation happens on the N2Sky platform and the ViNNSL Description file can be totally different, but the rules will be followed. The user now has a possibility to customize the structure, connection, metadata and parameters of the neural network. Due to restricted permissions of the ViNNSL template, it is impossible to mistype the schema.

The contributor user can also use ViNNSL in order to fill out the structure, connection, metadata and parameters of the neural network. If the user does it manually, without the N2Sky "3-step-view" generator, he has to upload his ViNNSL description in the N2Sky platform and the neural network will be automatically created. 

\subsubsection{Generated Metadata}\label{Generated metadata}

In the generated metadata, the information is filled out from N2Sky platform.

All unused fields will be removed automatically. The typical parameters, like "possibleValues", will be removed everywhere. The training parameters will remain the same.

 \begin{lstlisting}[caption=Generated ViNNSL model]
 ...
	"problemDomain": {
		"problemType": "Classifiers",
		"networkType": "Backpropagation",
		"applicationField": [
			"AccFin"
		],
		"propagationType": {
			"propType": "feedforward",
			"learningType": "supervised"
		}
	},
	"creator": {
		"name": "fedorenko",
		"contact": "andriifedorenko@gmail.com"
	},
	"metadata": {
		"name": "XOR Test",
		"description": "test",
		"paradigm": "Backpropagation",
...
\end{lstlisting}

The detailed information is shown in \autoref{B}

\subsubsection{Generated Structure}\label{Generated structure}

The structure is the most complicated part of the ViNNSL generation if the user does it manually without N2Sky generator. 

Every node will receive the id, which will be parsed by N2Sky.

\begin{itemize}
\item \emph{Input layer as well as output layer} have the same structure of the node ids.
 \begin{lstlisting}[caption=ViNNSL generated layers]
...
		"inputLayer": {
			"amount": 3,
			"nodesId": [
				"1-input",
				"2-input",
				"3-input"
			]
		},
		"outputLayer": {
			"amount": 1,
			"nodesId": [
				"1-output"
			]
		},
...
\end{lstlisting}

The amount of the nodes will be added. The nodes id has the following structure: 
\begin{enumerate}
\item The unique id of the node, which also defines the order
\item The name of the layer
\end{enumerate}
\item \emph{The hidden layer} can be multidimensional, that is why the id of the layer, as well as the id of nodes, are required.


 \begin{lstlisting}[caption=ViNNSL generated hidden layers]
...
		"hiddenLayer": [
			{
				"id": "1-hidden-layer",
				"amount": 4,
				"nodesId": [
					"1-node-1-hidden-layer",
					"2-node-1-hidden-layer",
					"3-node-1-hidden-layer",
					"4-node-1-hidden-layer"
				]
			},
...
\end{lstlisting}

The id of the layer is defined by the first number, which is also the order of the layer.

The id of the nodes is defined by the following rules:
\begin{enumerate}
\item The unique id of the node, which also defines the order
\item The id of the layer
\item The name of the layer
\end{enumerate}

\end{itemize}


\subsection{ViNNSL Model}\label{ViNNSL Model}

The ViNNSL Model derives from the ViNNL Description trained model. Basically, the input parameters were taken from the ViNNSL Description and default values were replaced with the trained data. Additionally, it was decided to put the following parameters:

\begin{itemize}
\item \emph{rawModel} is the raw training model, which can be used for the model evaluation. 
\item \emph{logs.} The logs are appending during training. When the training is done, the logs will be removed from the neural network and added as a parameter to the model.
\item \emph{test} is the array of performed tests. The test results are saved in the model in order to stop spreading multiple schemas. 
 \begin{lstlisting}[caption=ViNNSL trained model testing]
...
       {
                "createdOn": "2018-02-24T12:24:38.198Z",
                "result": "[[0.]\n [1.]\n [1.]\n [1.]]",
                "testing_data": "[[0,0],[0,1],[1,0],[1,1]]",
                "user": "admin"
            }
 ...
\end{lstlisting}
The test has following data:
\begin{itemize}
\item \emph{createdOn} timestamp of the testing
\item \emph{testing\_data} with which the model was tested
\item \emph{result} actual result of the testing
\item \emph{user} the user, who performed test.
\end{itemize}
\item \emph{paramters} the input parameters, where default values were replaced with the actual values. 
\end{itemize}

Detailed example of the ViNNSL model is located in \autoref{C}
